---
title: "lucky: enhanced common visualization and analysis tool for medicine researchers"
author: "Weibin Huang \\
         
         The First Affiliated Hospital,Sun Yat-sen University"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```


# Introduction

Medicine researchers are always disturbed by how to draw a publish-level plot for their medical project.Package lucky is a assembly functions of my own in daily use.It contains several critical modules as following.

+ Fast way to get plot of ggplot2 style
+ Fast way to do analysis for GEO database
+ Fast way to make bioinformatic analysis

## The theory of lucky package

### Name rule
Lower Camel Case is the most usual name rule in R programing.However,I plan to use Upper Camel Case,which is also another good choice but make lucky functions easier to be searched.It looks like `FastBar`,`FastExtra` and so on.

### Lucky structure
A good output of a standard publish-level object(including plot) should have these features:

+ outstanding visulization
+ individual environment for repetition
+ powerful debugger
+ easy function expansion

#### parameters
+ `save.file` whether to save file in present work space.
+ `names` part of the names of saved filed.If you set `names` like `lucky`,the name of output file would looks like `lucky_barplot.pdf`

#### design
This is defined by parameter `repeat` and output as an element of list
It is supported by `LuckyDebug` function as a S4 method
`repeat` the present parameters
`data` the important data of this function
`plot` the plot of the 





# Fast-Plot series

## FastBar
[see also](http://rpubs.com/loness/167347)

```{r,results = F}
library(lucky)
library(ggpubr)
# Data
df <- data.frame(dose=c("D0.5", "D1", "D2"),
                 len=c(4.2, 10, 29.5))
print(df)
```

`FastBar` is based on `ggpubr::ggboxplot`.
```{r,fig.show = "hold"}
# draw a barplot
FastBar(data = df,
        x = "dose",y = "len",
        fill = "dose",
        title = "Test_lucky::FastBar",
        legend.position = "right",
        size = 10)

# white fill
FastBar(data = df,
        x = "dose",y = "len",
        fill = "white", 
        title = "Test_lucky::FastBar",
        legend.position = "right",
        size = 10)

# no legend
FastBar(data = df,
        x = "dose",y = "len",
        fill = "white",
        title = "Test_lucky::FastBar",
        legend.position = "none",#with no legend
        size = 10)

## larger size
FastBar(data = df,
        x = "dose",y = "len",
        fill = "white",
        title = "Test_lucky::FastBar",
        legend.position = "none",#with no legend
        size = 15)

```





# Example
Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.


## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
